---
title: "Financial Reporting"
author: "Kevin Putschko"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
params:
  param_1: ^GSPC
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

pacman::p_load(tidyverse, lubridate, tidyquant, scales)
pacman::p_load_gh("rstudio/gt")

```

```{r get-data}
# Set symbol for lookup
symbol_lookup <- params$param_1
symbol_label <- symbol_lookup %>% str_remove("\\^")

# Get the data
symbol_data <- 
  symbol_lookup %>% 
  tq_get() %>% 
  arrange(desc(date))

```

## Introduction

In this document, we're going to pull stock information from the past two weeks for the **`r symbol_label`** stock symbol.  We're using the package `tidyquant` to easily pull this stock data from *Yahoo Finance*.  

## Stock Performance

The following table was created using the experimental `gt` package.  This package allows us to create headers, footers, references, while also formatting each column and adjusting the style as needed.  

We can easily pull values from this table and use it in this paragraph using R functions in the background.  For example, the most recent date, `r symbol_data$date[[1]]`, opened at `r symbol_data$open[[1]] %>% dollar()` and closed at `r symbol_data$close[[1]] %>% dollar()`.  These values will update on their own, and I'll never have to update this paragraph.  

```{r pretty-table}
# Use the last two weeks of data
date_now <- Sys.Date()
date_old <- date_now - days(15)

# Use html arrows for changes in stock
arrow_up <- "<span style=\"color:green\">&#9650;</span>"
arrow_down <- "<span style=\"color:red\">&#9660;</span>"

symbol_data %>% 
  filter(date >= date_old, 
         date <= date_now) %>% 
  select(-adjusted) %>% 
  gt() %>% 
  tab_header(title = symbol_label,
             subtitle = str_glue("{date_old} to {date_now}")) %>% 
  fmt_date(vars(date), date_style = 7) %>% 
  fmt_currency(vars(open, high, low, close), 
               currency = "USD") %>% 
  fmt_number(vars(volume), 
             scale_by = 1 / 1E9,
             pattern = "{x}B") %>% 
  text_transform(
    locations = cells_data(
      columns = "close",
      rows = close > open),
    fn = function(x) str_c(x, arrow_up, sep = " ")) %>% 
  text_transform(
    locations = cells_data(
      columns = "close",
      rows = close < open),
    fn = function(x) str_c(x, arrow_down, sep = " ")) %>% 
  cols_label(.list = 
               tibble(colnames(.), 
                      colnames(.) %>% str_to_title()) %>% 
               deframe()) %>% 
  tab_footnote(footnote = "*The **B** here refers to 'billion'*" %>% md(), 
               locations = cells_column_labels(vars(volume))) %>% 
  tab_source_note("Data comes from Yahoo Finance via `tidyquant` in R" %>% md())

```

## Charts

The following **candlestick** chart shows us the closing price of `r symbol_label` over the last 10 years. This chart was created using functions from the `tidyquant` package.

```{r chart}
symbol_data %>% 
  ggplot(aes(x = date, y = close)) +
  geom_candlestick(aes(open = open, high = high, low = low, close = close)) +
  labs(title = str_c(symbol_label, "Closing Price", sep = " "),
       subtitle = "Candlestick Chart",
       y = NULL, x = NULL) + 
  scale_y_continuous(labels = scales::dollar_format()) +
  theme_tq()
```

## Conclusion

R Markdown is easiest to use when output is stored as HTML.  In this way, RMD is useful for creating dashboards, websites, digital books, and HTML based presentations.
