---
title: "CRAN Package Downloads"
author: "Kevin Putschko"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warn = FALSE, message = FALSE)

pacman::p_load(tidyverse, lubridate, flextable, reactable, htmltools)
pacman::p_load_gh("metacran/cranlogs", "rstudio/gt")
```

```{r data-get}
data_raw <- 
  installed.packages()[ ,1] %>% 
  cran_downloads(when = "last-month") %>% 
  as_tibble()
```

# Introduction

This time around we're going to take a small look at the **reactable** package, which allows use to create interactive tables.  Note this will only work with HTML output format.  We're getting this data from CRAN, the central R repository for all R package libraries.  This table ranges from `r data_raw$date %>% min()` to `r data_raw$date %>% max()` and includes the Top 10 packages downloaded per week.

Notice we can click each row to expand the dates, and each package name is a clickable link to the CRAN page for that particular package.


```{r table-gt}
# dates_weekday <- 
#   data_raw %>% 
#   distinct(date) %>% 
#   mutate(weekday = wday(date, label = TRUE),
#          weekend = if_else(weekday %in% c("Sat", "Sun"), "Weekend", "Weekday")) %>% 
#   select(-weekday) %>% 
#   chop(date) %>% 
#   deframe() %>% 
#   map(format, "%Y-%m-%d")
# 
# data_raw %>% 
#   spread(date, count) %>% 
#   gt(rowname_col = "package") %>% 
#   tab_header("Download Count of Individual Tidyverse Packages",
#              subtitle = str_glue("Between dates {data_raw$date %>% min()} and {data_raw$date %>% max()}")) %>% 
#   fmt_number(TRUE, decimals = 0) %>% 
#   tab_stubhead("Packages") %>% 
#   tab_options(
#     column_labels.font.size = "smaller",
#     table.font.size = "smaller",
#     row.padding = px(5)
#   ) %>% 
#   tab_spanner(label = "Weekend",
#               columns = dates_weekday$Weekend) %>% 
#   tab_spanner(label = "Weekday",
#               columns = dates_weekday$Weekday) %>% 
#   summary_rows(fns = list("Daily Total" = "sum"), 
#                decimals = 0)
```

```{r table-long}
# data_raw %>%
#   gt(groupname_col = "package",
#      rowname_col = "date") %>%
#   tab_header("Download Count of Individual Tidyverse Packages",
#              subtitle = str_glue("Between dates {data_raw$date %>% min()} and {data_raw$date %>% max()}")) %>%
#   fmt_number(columns = TRUE, decimals = 0) %>%
#   summary_rows(groups = TRUE,
#                fns = list('Package Total' = "sum"),
#                formatter = fmt_number, decimals = 0) %>%
#   tab_options(
#     summary_row.background.color = "#ACEACE",
#     row_group.background.color = "#FFEFDB"
#   )
```

```{r table-rt, warning=FALSE}
data_raw %>% 
  mutate(week = isoweek(date)) %>% 
  group_by(week) %>% 
  mutate(label = str_glue("Week {week}: {min(date) %>% format('%m/%d/%Y')} - {max(date) %>% format('%m/%d/%Y')}")) %>% 
  group_by(label, package) %>% 
  summarise(sum = sum(count)) %>% 
  arrange(label, -sum) %>%
  top_n(10, sum) %>% 
  ungroup() %>% 
  reactable(outlined = TRUE,
            striped = TRUE,
            highlight = TRUE,
            groupBy = "label",
            columns = list( 
              label = colDef(name = "Week", width = 350),
              package = colDef("Top 10 Packages",
                               cell = function(value, index){
                                 url <- str_glue("https://cran.r-project.org/web/packages/{.[index, 'package']}/index.html")
                                 htmltools::tags$a(href = url, target = "_blank", as.character(value))
                               }),
              sum = colDef(name = "Downloads",
                           aggregate = "sum",
                           defaultSortOrder = "desc",
                           format = colFormat(separators = TRUE),
                           # cell = function(value){
                           #   width <- value / max(.$value)
                           #   bar <- div(class = "bar-chart",
                           #              style = list(marginRight = "6px"),
                           #              div(class = "bar", style = list(width = width, backgroundColor = "#3fc1c9")))
                           #   
                           #   div(class = "bar-cell", span(class = "number", value), bar)
                           # }
              )
            )
  )
```
