---
title: "LaTeX PDF Output"
author: "Kevin Putschko"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  pdf_document:
    toc: yes
    extra_dependencies: ["lastpage", "pdflscape", "fancyhdr"]
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage[normalem]{ulem}
params:
  param_1: Kevin Putschko
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(kableExtra.latex.load_packages = FALSE)

pacman::p_load(tidyverse, knitr, kableExtra, scales)

# username <- params$param_1
username <- "Kevin Putschko"
```

\pagestyle{fancy}

\lhead{\textit{`r username`}}
\rhead{PDF LaTeX}

\cfoot{}
\rfoot{Page \thepage\ of\ \pageref{LastPage}}
\lfoot{User: `r username` \\ Date: \today \\ Source: a/file/path.txt}

\newcommand{\bls}{\begin{landscape}}
\newcommand{\els}{\end{landscape}}


\newpage
# Introduction

`LaTeX` is a type setting system built for technical or scientific documents in the 1970's.  To use it with R, you'll need to install one of a handful of Latex packages, like `tinytex`.  

We use `LaTeX` with RMD here because it is simple to incorporate into an R Markdown document once you get the hang of the syntax.

This only works with PDF output, but it is quite flexible.  In the `R Markdown` document itself, we can load various `LaTeX` packages and include their functions with a simple call like `\rfoot` to place a footer in the lower right corner of the page.  

\newpage
# Wide Output, Landscape

Here we rotate the page to landscape using the `pdflscape` package.  Note, however, that the headers and footers are not in ideal locations for this layout.  However, we do see that the table does stretch to a second page, while retaining the headers.  

```{r wide-table}
dplyr::storms %>% 
  slice(1:50) %>% 
  kable(longtable = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("repeat_header")) %>% 
  landscape()
```


\newpage
# Wide Output, Portrait

However, if we just want to scale the table down to fit on a portrait orientation, we can use the `scale_down` option in `kableExtra`.

```{r shrink-table}
dplyr::storms %>% 
  slice(1:50) %>% 
  kable(format = "latex") %>%
  kable_styling(latex_options = c("repeat_header", "scale_down"))
```

\newpage
# Many Tables

Now we're using a loop to output many tables from one master table, using the `kableExtra` package.

```{r many-tables, results='asis'}
table_nest <-
  dplyr::storms %>% 
  group_by(year, status) %>% 
  count() %>%
  group_by(year) %>% 
  mutate(p = n / sum(n),
         p = percent(p),
         status = str_to_title(status)) %>% 
  ungroup() %>% 
  group_nest(year, .key = "table", keep = TRUE) %>% 
  deframe()

for (i in 1:length(table_nest)) {
  
  table_label <- table_nest[[i]] %>% filter(n == max(n))
  table_year  <- table_label %>% pluck("year")
  table_storm <- table_label %>% pluck("status") 
  table_days  <- table_label %>% pluck("n") 
  
  table_nest[[i]] %>% 
    kable(format = "latex", 
          booktabs = TRUE, 
          longtable = TRUE, 
          caption = str_glue("Year {table_year}"),
          label = str_c("Table ", i),
          col.names = c("", "Type of Storm", "Days per Year", "Percent of Storms")) %>% 
    column_spec(3:4, width = "3cm") %>% 
    row_spec(0, bold = TRUE) %>% 
    collapse_rows(columns = 1, valign = "middle") %>% 
    kable_styling(latex_options = "repeat_header") %>% 
    print()
  
  str_glue("This text is located within the loop.  We can pull out some values from this table.  For example,
      the type of storm that occured most in the year {table_year} 
      is a **{table_storm}** which was present over {table_days} days!") %>% 
  cat()
  
  # Notice the two spaces and double backslash to register both a newline and a latex function
  cat("  \\newpage")
  
}

```


\newpage
# Conclusion

I like the potential of `LaTeX` and PDF output!  Easy to create tables, and customize the pages.  Only issue is the landscape page with rotated headers and footers.

