---
title: "Clinical Data"
author: "Kevin Putschko"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  word_document: 
    toc: yes
    pandoc_args:
      '--lua-filter=pagebreak.lua'
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
# Note in the above YAML config
# doc does not, so we add an outside function definition, located in project dir
# word_document:
#     pandoc_args:
#       '--lua-filter=pagebreak.lua'

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
pacman::p_load(tidyverse, haven, flextable, scales)
data_dem <- read_sas("data/David Bosak/demog.sas7bdat")

```

```{r data-prep}

# The base table we'll be using
data_demog_table_base <- 
  data_dem %>% 
  select(TRTC, AGE, AGEC, SEX, RACE) %>% 
  group_by(TRTC)
  

# Split by categorical and numeric
data_demog_table_numeric <- 
  data_demog_table_base %>% 
  summarise_if(is.double, .funs = c("length", "median", "mean", "sd", "min", "max")) %>% 
  mutate(str_mean = number(mean, trim = FALSE),
         str_sd = number(sd, accuracy = 0.1, trim = FALSE),
         N = number(length),
         `Mean (SD)` = str_glue("{str_mean} ({str_sd})") %>% as.character(),
         Median = number(median, accuracy = 0.1),
         Range = str_c(min, max, sep = "-")) %>% 
  select(TRTC, N:Range) %>% 
  pivot_longer(-TRTC, 
               names_to = "label",
               values_to = "str_value") %>% 
  pivot_wider(names_from = TRTC, 
              values_from = str_value) %>% 
  mutate(demo = "AGE") # This will have to be adjusted with more numeric cols

data_demog_table_category <- 
  data_demog_table_base %>% 
  select(-AGE) %>% # Change this when more numeric cols are present 
  pivot_longer(-TRTC, names_to = "demo", values_to = "label") %>% 
  count(TRTC, demo, label) %>%
  group_by(TRTC, demo) %>% 
  mutate(p = n / sum(n)) %>% 
  ungroup() %>% 
  mutate(str_n = number(n, trim = FALSE),
         str_p = percent(p, 0.1, trim = FALSE),
         str_value = str_glue("{str_n} ({str_p})")) %>% 
  select(TRTC, demo, label, str_value) %>%
  spread(TRTC, str_value)


# Get grand totals
data_demog_table_totals_cat <- 
  data_demog_table_base %>% 
  ungroup() %>% 
  select(-AGE, -TRTC) %>% # Change this when more numeric cols are present 
  pivot_longer(cols = everything(), names_to = "demo", values_to = "label") %>% 
  count(demo, label) %>%
  group_by(demo) %>% 
  mutate(p = n / sum(n)) %>% 
  mutate(str_n = number(n, trim = FALSE),
         str_p = percent(p, 0.1, trim = FALSE),
         str_value = str_glue("{str_n} ({str_p})")) %>% 
  mutate(TRTC = "Grand Total") %>% 
  select(TRTC, demo, label, str_value) %>% 
  spread(TRTC, str_value) 
  
data_demog_table_totals_num <- 
  data_demog_table_base %>% 
  ungroup() %>% 
  summarise_at("AGE", .funs = c("length", "median", "mean", "sd", "min", "max")) %>% 
  mutate(str_mean = number(mean, trim = FALSE),
         str_sd = number(sd, accuracy = 0.1, trim = FALSE),
         N = number(length),
         `Mean (SD)` = str_glue("{str_mean} ({str_sd})") %>% as.character(),
         Median = number(median, accuracy = 0.1),
         Range = str_c(min, max, sep = "-")) %>% 
  select(N:Range) %>% 
  pivot_longer(cols = everything(),
               names_to = "label",
               values_to = "Grand Total") %>% 
  mutate(demo = "AGE") # This will have to be adjusted with more numeric cols


# Create final summary table
data_demog_table_full_summary <- 
  bind_rows(data_demog_table_category,
            data_demog_table_numeric) %>% 
  left_join(
    bind_rows(data_demog_table_totals_cat,
              data_demog_table_totals_num)) %>% 
  arrange(demo) %>% 
  ungroup() %>% 
  mutate(demo = ifelse(demo == "AGEC", "Age Group", str_to_title(demo)))

```

\newpage

# Introduction

This time we'll be using **`flextable`** to create the summary table.  This package is meant to create tables for **Microsoft Office** output, and is part of the `officer` family of packages.  The caveat here is that this package does not do any transformations of the data, so all the summary work needs to be done in advance.  This package simply helps with the formatting and styles of the table.

\newpage

# Demographics

Here we see the `flextable` output.  

```{r flextable}
# FT does not allow for data transformations!

data_demog_table_full_summary %>% 
  as_grouped_data("demo") %>% 
  flextable() %>% 
  set_header_labels(demo = "", label = "") %>% 
  autofit() %>% 
  bold(part = "header") %>% 
  bold(part = "body", j = "demo") %>% 
  # italic(part = "body", j = "label") %>% 
  fontsize(j = "label", size = 9) %>% 
  vline(j = "`Drug C`", border = officer::fp_border()) %>% 
  add_header_lines(values = "Table 1.0 - Patient Demographics") %>% 
  add_footer_lines(values = c("User: KP", str_glue("Date: {Sys.time()}")))
  
```


